---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: This is just a toy package. Made by following the book: `R Packages` from Hadley Wickham.
# Freekfoofactors

Contains two functions for working with factors.

## Installation


``` {r installation, eval = F}
devtools::install_github("FreekManders/foofactors")
```

## Demo

```{r}
library(Freekfoofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
```

The `fcount()` function returns a frequency table as a tibble with a column of factor levels and another of frequencies:

```{r}
fcount(x)
```
